Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to test combining the positive depression and anxiety positive diagnoses for GLAD/EDGI prepan
cbinded all the positive diagnoses for GLAD/EDGI prepan

>>>>

```{r}

GLAD.prepan_positive_diagnosis_GLADEDGI <- GLAD.prepan_mdd_positive %>% 
  cbind(GLAD.prepan_anxi_positive,
        GLAD.prepan_ED_positive,
        GLAD.prepan_OCD_positive,
        GLAD.prepan_psychosis_positive,
        GLAD.prepan_ASD_positive,
        GLAD.prepan_ADHD_positive,
        GLAD.prepan_PD_positive,
        GLAD.prepan_BD_positive,
        GLAD.prepan_PTSD_positive,
        GLAD.prepan_control_positive)

head(GLAD.prepan_positive_diagnosis_GLADEDGI)
